SVG: The Paper

### 2022-05-04 Analysis/index.Rmd
graph edit

plt_b + plt_c + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom',
        legend.direction = 'horizontal')

@@

ggplot(a_acc, aes(x= condition, y = accuracy, fill = condition)) + 
  geom_boxplot() +
  geom_line(aes(group = observer), alpha = 0.25, colour = "sienna4") +
  scale_y_continuous("model accuracy",  
                     limits = c(0.3, 0.8), breaks = seq(0.3, 0.8, 0.1)) -> plt_a

@@

plt_b <- ggplot(filter(fit_plt, parameter == "bP"), 
                aes(value, accuracy, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(fit_plt, is_outlier == 0, parameter == "bP"), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  theme(legend.position = "bottom")

ggsave("../Figures/qjep_indiv_diff.png", 
       plt_a + plt_b + 
         plot_layout(guides = "collect") & theme(legend.position = "bottom"), width = 8, height = 4)
```

>>>>

plt_b + plt_c + plot_layout(guides = "collect")  &
  theme(legend.position = 'right',
        legend.direction = 'horizontal')

@@

ggplot(a_acc, aes(x= condition, y = accuracy, fill = condition)) + 
  geom_boxplot() +
  geom_line(aes(group = observer), alpha = 0.25, colour = "sienna4") +
  scale_y_continuous("model accuracy",  
                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1)) -> plt_a

@@

plt_b <- ggplot(filter(fit_plt, parameter == "bP"), 
                aes(value, accuracy, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(fit_plt, is_outlier == 0, parameter == "bP"), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  theme(legend.position = "none") + 
   scale_y_continuous("model accuracy",  
                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1))

ggsave("../Figures/qjep_indiv_diff.png", 
       plt_a + plt_b + 
         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
```
